Forecasting the old-age dependency ratio to determine the best pension age

### 2020-09-17 PensionAge.Rmd
Refactored to use drake

---
title: "Forecasting the old-age dependency ratio to determine the best pension age"
author:
- familyname: Hyndman
  othernames: Rob J
  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
  email: Rob.Hyndman@monash.edu
  correspondingauthor: true
- familyname: Zeng
  othernames: Yijun
  address: Monash University
- familyname: Shang
  othernames: Han Lin
  address: Macquarie University
abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population. We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the 2018 level, which is 21%. This approach can easily be extended to other target levels of the old-aged dependency ratio and other countries."
keywords: "coherent forecasts, demographic components, functional time series model, pension and insurance"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: true
toc: false
bibliography: pensionage.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
header-includes:
  - \usepackage{todonotes, xcolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(demography)
library(patchwork)
source("functions-v4.R")
```

@@

```{r changespension, echo=FALSE, fig.cap="Australian pension age policies.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
# Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
# Law: https://guides.dss.gov.au/guide-social-security-law/3/4/1/10
# History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
pension_age <- tibble(
  Year = 1920:2068,
  Current = 65
) %>%
  mutate(
    Proposed = pmin(70, Current + 0.5 * pmax(0, trunc((Year - 2015) / 2))),
    Approved = pmin(Proposed, 67),
  ) %>%
  pivot_longer(-Year, values_to = "Age", names_to = "Policy")

pension_age %>%
  filter(Year >= 2008, Year <= 2050) %>%
  ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
  geom_line() +
  ylab("Minimum pension age") +
  scale_color_brewer(
    palette = "Dark2",
    breaks = c("Proposed", "Approved", "Current"),
    labels = c("Proposed further change", "Approved change", "Pension age at 65")
  )
```

@@

The data used are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year. Let
\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
\end{align*}
where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study. The year is denoted by $t=1,2,\dots,n$, and superscripts $M$ and $F$ denote male and female respectively.

@@

Using this notation, the OADR in year $t$ is given by
\begin{equation}\label{eq:oadr}
\text{OADR}_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
\end{equation}
where $a_t$ is the pension age and $r_t = a_t - \lfloor a_t \rfloor$ is the non-integer part of $a_t$. This assumes that the pension age can only be adjusted at the beginning of a year, and that the birthday of the population is uniformly distributed over the year.

@@

The model is over-parameterised. Therefore, the constraints
\begin{equation}
  \sum_{t=1}^{n}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
\end{equation}
are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} [@Good1969]. The estimates of $\phi(x)$ and $\beta_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{t}(x))-\widehat\mu(x)]$, where $\widehat\mu(x)$ is the sample mean of $\log(m_{t}(x))$ over $t$. The log transformation introduces some bias, so the LC method adjusts $\beta_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths. The adjusted $\beta_t$ is then extrapolated using a random walk with drift model.

@@

By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{n+h}(x)$ are given by
\begin{equation}
  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j},
\end{equation}
where $\widehat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$. Because $\left\{\beta_{t,j}\right\}$ is time-varying, it controls the dynamics of the process. Each component series $\left\{\beta_{t,j}\right\}$ is modelled with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are selected using the automated algorithm of @forecastpackage, and the parameters are estimated using maximum likelihood estimation.

@@

When we apply the @HU07 model to data on males and females, we need to constrain the resulting forecasts so they do not diverge. In the product-ratio method [@HBY13], the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently. That is, define
\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}
Then, the HU method is applied to these two new variables:
\begin{align*}
  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with ARIMA models while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecasts of male and female do not diverge. Then, forecasts of sex-specific data are obtained using
\begin{align*}
  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.

@@

This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a sample path of the age-specific population. Many simulated population paths were obtained in this way. For each simulated population path, and each proposed set of pension age changes, we can simulate future OADR values using \eqref{eq:oadr}.

@@

```{r getdata, eval=FALSE}
################################################
################### DATA STEP ##################
################################################

# Get population data to 1 Jan 2019
source("hmd.R") # File only stores username and password
aus.pop <- hmd.pop(
  country = "AUS", username = username, password = password,
  label = "Australia"
)
aus.pop <- extract.ages(aus.pop, ages = 0:100)

# Get mortality data to 2018
aus.mort <- hmd.mx("AUS", username, password, "Australia")
aus.mort <- aus.mort %>%
  extract.ages(ages = 0:100, combine.upper = FALSE) %>%
  extract.years(years = 1950:max(aus.mort$year))

# Get fertility data for 1921-2006
aus.fert <- addb::aus.fertility
births <- aus.fert$rate$female * aus.fert$pop$female
# Get latest fertility data from ABS (downloaded 30 April 2020)
ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
  filter(
    Region == "Australia",
    Age %in% paste(15:49),
  ) %>%
  mutate(
    Year = Time,
    Age = as.numeric(Age)
  ) %>%
  select(Year, Age, Measure, Value)
# Extract births and population values
newbirths <- ausf %>%
  filter(Measure == "Births") %>%
  mutate(Value = Value * 1000) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
newpop <- ausf %>%
  filter(Measure == "Female population") %>%
  mutate(Value = Value) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
rownames(newbirths) <- rownames(newpop) <- 15:49

# Use ABS data where available
births <- cbind(births[, 1:54], newbirths)
fpop <- cbind(aus.fert$pop$female[, 1:54], newpop)
# Use populations in ausf rather than aus.pop to get the same rates
aus.fert$rate$female <- births / fpop
aus.fert$pop$female <- fpop
aus.fert$year <- 1920 + seq(NCOL(births))

# Compute migration data
aus.mig <- netmigration(
  mort = aus.mort, fert = aus.fert,
  startyearpop = aus.pop, mfratio = 1.05
)
save(aus.fert, aus.mort, aus.mig, aus.pop, file = "ausdata.Rdata")
rm(ausf, births, fpop, newbirths, newpop)
```

```{r maketibble}
load("ausdata.Rdata")

auspop_df <- bind_rows(
  as_tibble(aus.pop$pop$male / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Male"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  as_tibble(aus.pop$pop$female / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Female"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
)
```

```{r smoothing}
################################################
################ SMOOTHING STEP ################
################################################

ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
ausfert.sm <- smooth.demogdata(aus.fert, obs.var = "theoretical")
ausmig.sm <- smooth.demogdata(aus.mig)
```

```{r models, dependson='smoothing'}
################################################
################ MODELLING STEP ################
################################################

# MORTALITY
mort.fit <- coherentfdm(ausmort.sm)
mortf <- forecast(mort.fit, h = 50)

# FERTILITY
fert.fit <- fdm(ausfert.sm)
fertf <- forecast(fert.fit, h = 50)

# MIGRATION
mig.fit <- coherentfdm(ausmig.sm)
migf <- forecast(mig.fit, h = 50)
```

@@

```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models', message=FALSE}
autoplot(fertf)
```

@@

```{r simulation, dependson='models'}
############### SIMULATION STEP #################
if(file.exists("aus_sim.rds")) {
  aus.sim <- readRDS("aus_sim.rds")
} else {
  # This takes a while!
  set.seed(2020 - 05 - 02)
  nsim <- 2000 # Change to 2000 or higher to get better estimates
  aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = aus.pop, N = nsim)
  saveRDS(aus.sim, "aus_sim.rds")
}
```

```{r sim_tibbles, dependson='simulation'}
# Combine simulation results into one tibble
dimnames(aus.sim[["male"]]) <- dimnames(aus.sim[["female"]]) <- list(
  Age = dimnames(aus.sim[[1]])[[1]],
  Year = as.numeric(dimnames(aus.sim[[1]])[[2]]) + 1,
  Rep = dimnames(aus.sim[[1]])[[3]]
)
aussim_df <- bind_rows(
    as.tbl_cube(aus.sim[["male"]] / 1e3, met_name = "Population") %>%
      as_tibble() %>% mutate(Sex = "Male"),
    as.tbl_cube(aus.sim[["female"]] / 1e3, met_name = "Population") %>%
      as_tibble() %>% mutate(Sex = "Female")
  )

# Combine simulations to create means and quantiles of future years
future_pop <- aussim_df %>%
  group_by(Sex, Age, Year) %>%
  summarise(
    Mean = mean(Population),
    Lower = quantile(Population, prob = 0.1),
    Upper = quantile(Population, prob = 0.9)
  ) %>%
  ungroup()
# Historical data as a tibble
history_pop <- bind_rows(
  as_tibble(aus.pop$pop$male / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Male"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
  as_tibble(aus.pop$pop$female / 1000) %>%
    mutate(
      Age = aus.pop$age,
      Sex = "Female"
    ) %>%
    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
) %>%
  mutate(Year = as.numeric(Year))
```

```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.", fig.height=4, dependson='simulationresults'}
future_tot_pop <- aussim_df %>%
  group_by(Rep, Sex, Year) %>%
  summarise(Population = sum(Population) / 1e3) %>%
  group_by(Sex, Year) %>%
  summarise(
    Mean = mean(Population),
    Median = median(Population),
    Lo95 = quantile(Population, prob = 0.025),
    Up95 = quantile(Population, prob = 0.975),
    Lo80 = quantile(Population, prob = 0.1),
    Up80 = quantile(Population, prob = 0.9)
  ) %>%
  ungroup()
history_pop %>%
  group_by(Sex, Year) %>%
  summarise(Population = sum(Population) / 1e3) %>%
  ggplot(aes(x = Year, y = Population, group = Sex)) +
  geom_line(size = 1) +
  ylab("Population (millions)") +
  ggtitle("Total population") +
  facet_grid(. ~ Sex) +
  geom_ribbon(aes(y = Mean, ymin = Lo80, ymax = Up80), fill = "#7d7def", data = future_tot_pop) +
  geom_line(data = future_tot_pop, col = "#0000cc", mapping = aes(y = Mean), size = 1)
```

```{r totalpopulationin2038, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
pyramid <- function(history, future) {
  data <- bind_rows(history, future)
  p_male <- data %>%
    filter(Sex == "Male") %>%
    ggplot(aes(x = Age, y = Population, group = Year)) +
    labs(y = "Population ('000)") +
    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
    geom_line(linetype = 2) +
    geom_line(aes(y = Mean), col = "#0000cc") +
    coord_flip() +
    scale_y_reverse(expand = c(0.012, 0.012)) +
    scale_x_continuous(expand = c(0.012, 0.012)) +
    facet_grid(. ~ Sex)
  p_female <- data %>%
    filter(Sex == "Female") %>%
    ggplot(aes(x = Age, y = Population, group = Year)) +
    labs(y = "Population ('000)") +
    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
    geom_line(linetype = 2) +
    geom_line(aes(y = Mean), col = "#0000cc") +
    coord_flip() +
    scale_y_continuous(expand = c(0.012, 0.012)) +
    theme(
      axis.title.y.left = element_blank(),
      axis.text.y.left = element_blank(),
      axis.ticks.y.left = element_blank()
    ) +
    scale_x_continuous(position = "top", sec.axis = sec_axis(~.), expand = c(0.012, 0.012)) +
    facet_grid(. ~ Sex)

  (p_male | p_female)
}
pyramid(
  history_pop %>% filter(Year == max(Year)),
  future_pop %>% filter(Year == max(history_pop$Year) + 20)
)
```

@@

Historical OADR values are shown in Figure \@ref(fig:OADRcurrent) for 1921--2019. The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 [@IGR02] and 2007 [@IGR07]. The increased trend from 2010 is due to the retirements of "Baby Boomers", born after WW2. We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise 6 months every two years until it reaches 70 in 2035.

```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple). The actual OADRs for 1921--2019 are shown in black.", dependson='OADRcurrent'}
OADR_history <- oadr(history_pop, filter(pension_age, Policy == "Current"))
OADR.65 <- oadr_sim(aussim_df, filter(pension_age, Policy == "Current")) %>%
  mutate(Policy = "Pension age 65")
df <- bind_rows(
  OADR.65,
  oadr_sim(aussim_df, filter(pension_age, Policy == "Approved")) %>%
    mutate(Policy = "Current policy"),
  oadr_sim(aussim_df, filter(pension_age, Policy == "Proposed")) %>%
    mutate(Policy = "Proposed policy")
) %>%
  mutate(Policy = factor(Policy,
    levels = c("Pension age 65", "Current policy", "Proposed policy")
  ))
df %>%
  ggplot(aes(x = Year, y = OADR)) +
  geom_hline(yintercept = 0.25, col = "gray") +
  geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy), alpha = 0.5) +
  geom_line(aes(col = Policy, group = Policy), size = .75) +
  geom_line(col = "black", size = .75, data = OADR_history) +
  xlab("year") +
  ylab("ratio") +
  ggtitle("OADR forecasts with pension age=65") +
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")
```

@@

# Finding the target pension age scheme {#sec:target}

>>>>

---
title: "Forecasting the old-age dependency ratio to determine the best pension age"
author:
- familyname: Hyndman
  othernames: Rob J
  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
  email: Rob.Hyndman@monash.edu
  correspondingauthor: true
- familyname: Zeng
  othernames: Yijun
  address: Monash University
- familyname: Shang
  othernames: Han Lin
  address: Macquarie University
abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population. Our results suggest that the Australian pension age should be increased to 68 by 2028 and 69 by 2034 in order to maintain the old-age dependency ratio at 23%, just above the 2018 level. Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
keywords: "coherent forecasts, demographic components, functional time series model, pension and insurance"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: true
toc: false
bibliography: pensionage.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
header-includes:
  - \usepackage{todonotes, xcolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = FALSE)

# Set up drake plan
source("_drake.R")

# Run all code required
drake::r_make()

# Load results
drake::loadd()

# Load additional packages for graphs and tables
library(ggplot2)
library(patchwork)
```

@@

```{r changespension, echo=FALSE, fig.cap="Australian pension age policies.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
# Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
# Law: https://guides.dss.gov.au/guide-social-security-law/3/4/1/10
# History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
pension_age %>%
  filter(Year >= 2014) %>%
  ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
    geom_line() +
    ylab("Minimum pension age") +
    scale_color_brewer(
      palette = "Dark2",
      breaks = c("Proposed", "Current", "Age65"),
      labels = c("Proposed further change", "Current policy", "Pension age at 65")
    )
```

@@

The data used are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year. Let
\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
\end{align*}
where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study. The year is denoted by $t=1,2,\dots,T$, and superscripts $M$ and $F$ denote male and female respectively.

@@

Using this notation, the OADR in year $t$ is given by
\begin{equation}\label{eq:oadr}
O_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
\end{equation}
where $a_t$ is the pension age in year $t$ and $r_t = a_t - \lfloor a_t \rfloor$ is the non-integer part of $a_t$. This assumes that the pension age can only be adjusted at the beginning of a year, and that the birthday of the population is uniformly distributed over the year.

@@

The model is over-parameterised. Therefore, the constraints
\begin{equation}
  \sum_{t=1}^{T}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
\end{equation}
are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} [@Good1969]. The estimates of $\phi(x)$ and $\beta_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{t}(x))-\widehat\mu(x)]$, where $\widehat\mu(x)$ is the sample mean of $\log(m_{t}(x))$ over $t$. The log transformation introduces some bias, so the LC method adjusts $\beta_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths. The adjusted $\beta_t$ is then extrapolated using a random walk with drift model.

@@

By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{T+h}(x)$ are given by
\begin{equation}
  \widehat{y}_{T+h\mid T}(x)=\widehat{s}_{T+h\mid T}(x) = \text{E}[\widehat{s}_{T+h\mid T}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{T+h\mid T,j},
\end{equation}
where $\widehat{\beta}_{T+h\mid T,j}$ denotes the $h$-step-ahead forecast of $\beta_{T+h\mid T,j}$. Because $\left\{\beta_{t,j}\right\}$ is time-varying, it controls the dynamics of the process. Each component series $\left\{\beta_{t,j}\right\}$ is modelled with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are selected using the automated algorithm of @forecastpackage, and the parameters are estimated using maximum likelihood estimation.

@@

When we apply the @HU07 model to data on males and females, we need to constrain the resulting forecasts so they do not diverge. In the product-ratio method [@HBY13], the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently. That is, define
\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}
Then, the HU method is applied to these two new variables:
\begin{align*}
  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with ARIMA models while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecasts of male and female do not diverge. Then, forecasts of sex-specific data are obtained using
\begin{align*}
  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x)\\
  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x)
\end{align*}
The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.

@@

This simulation was repeated for years $t=T+1,\dots,T+h$ to obtain a sample path of the age-specific population. Many simulated population paths were obtained in this way. For each simulated population path, and each proposed set of pension age changes, we can simulate future OADR values using \eqref{eq:oadr}.

@@

@@

```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", message=FALSE}
autoplot.fmforecast(fertf)
```

@@

```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.", fig.height=4}
history_pop %>%
  group_by(Sex, Year) %>%
  summarise(Population = sum(Population) / 1e3) %>%
  ggplot(aes(x = Year, y = Population, group = Sex)) +
    geom_line(size = 1) +
    ylab("Population (millions)") +
    ggtitle("Total population") +
    facet_grid(. ~ Sex) +
    geom_ribbon(aes(y = Mean, ymin = Lo80, ymax = Up80), fill = "#7d7def", data = future_tot_pop) +
    geom_line(data = future_tot_pop, col = "#0000cc", mapping = aes(y = Mean), size = 1)
```

```{r totalpopulationin2038, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE}
pyramid(
  history_pop %>% filter(Year == max(Year)),
  future_pop %>% filter(Year == max(history_pop$Year) + 20)
)
```

@@

Historical OADR values are shown in black in Figure \@ref(fig:OADRcurrent) for 1921--2019. The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 [@IGR02] and 2007 [@IGR07]. The increased trend from 2010 is due to the retirements of "Baby Boomers", born after WW2. We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.

```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple). The actual OADRs for 1921--2019 are shown in black."}
OADR_future %>%
  ggplot(aes(x = Year, y = OADR)) +
    geom_hline(yintercept = target, col = "gray") +
    geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy),
      alpha = 0.5) +
    geom_line(aes(col = Policy, group = Policy), size = .75) +
    geom_line(col = "black", size = .75, data = OADR_history) +
    xlab("year") +
    ylab("ratio") +
    ggtitle("OADR forecasts with pension age=65") +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2")
```

@@

# Sustainable pension age scheme

Our aim is to determine a pension age scheme that would lead to the OADR being below a desired threshold, thus imposing a sustainability constraint.

Let $a_t$ denote the pension age in year $t$, and we denote a pension age scheme over the prediction horizon by $\bm{P}=[a_{T+1},\dots,a_{T+H}]'$, with the corresponding OADR values given by $O_{T+1},\dots,O_{T+H}$. Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold.  We impose the constraint $0 \le a_t - a_{t-1} < 1$ to prevent two undesirable situations: (a) years where no-one is able to retire; and (b) years where retired people become ineligible for the pension. We also assume that the adjustment unit of the pension age is one month, for easier implementation.

## Finding the target pension age scheme {#sec:target}

Let $O^*$ denote the desired OADR threshold. Because we do not observe the population in future years, we must estimate $O_{T+h}$ from the simulated populations. Then we compute the pension age scheme $\bm{P}$ using the following algorithm. Starting with $h=1$:

  1. Set $a_{T+h}=a_{T+h-1}$.
  2. Increment $a_{T+h}$ by one-month intervals until either $\widehat{O}_{T+h|T} > O^*$ or $a_{T+1} - a_{T}=$ 1 month, where $\widehat{O}_{T+h|T}$ denotes the mean of the simulated $O_{T+h|T}$ values.

We repeat these steps for $h=2,\dots,H$.

In addition to finding the target pension age based on the mean value of OADR, we also find "plausible" pension age schemes that could give the desired OADR level. Specifically, we find a range of pension age schemes for which $O^*$ is contained within the 80% prediction intervals of the simulated $O_{T+H|T}$ values. Because of the monotonic relationship between pension age and OADR, we need only to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level. Hence, any pension age scheme within those two boundaries is plausible. The range of plausible pension age schemes can be thought of as an 80% confidence interval of pension age schemes where we are 80% sure that they will give the desired outcome.

The algorithm to find the upper and lower boundary of plausible pension age schemes is the same as above, but mean of $O_{T+H|T}$ is replaced by the 10% and 90% quantiles.

```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by the government, along with the 80% confidence interval of the target pension age shown in the green shade. The solid red line indicates the changes to the pension age from 65 to 67, announced in 2009."}
pension.fc <- structure(
  list(
    mean = ts(pension_age_optimal$Age, start = min(pension_age_optimal$Year)),
    lower = ts(as.matrix(pension_age_lower$Age), start = min(pension_age_optimal$Year)),
    upper = ts(as.matrix(pension_age_upper$Age), start = min(pension_age_optimal$Year)),
    level = 80
  ),
  class = "forecast"
)
ggplot() +
  autolayer(pension.fc, series = paste("Pension age to give OADR =", target)) +
  autolayer(
    ts(pension_age %>% filter(Policy == "Current", Year >= 1995) %>% pull(Age),
       start = 1995),
    series = "Approved change"
  ) +
  autolayer(
    ts(pension_age %>% filter(Policy == "Age65", Year >= 1995) %>% pull(Age),
      start = 1995),
    series = "Pension age at 65"
  ) +
  xlab("Year") +
  ylab("Minimum pension age")
```

```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2018). The 80% prediction interval of the forecast of OADR is shown as blue shading."}
## plots of OADR with plausible pension age schemes
OADR_optimal %>%
  ggplot(aes(x = Year)) +
    geom_hline(yintercept = target, col = "red") +
    geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
    geom_line(aes(y = OADR), col = "#0000cc") +
    geom_line(data = OADR_history, aes(y = OADR)) +
    ggtitle("OADR forecast estimates for optimal pension ages") +
    ylab("Old age dependency ratio")
```

```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes (listed in Table 2), along with desired OADR level (in red)."}
bind_rows(
    OADR_upper %>% mutate(Series = "Upper boundary"),
    OADR_lower %>% mutate(Series = "Lower boundary"),
  ) %>%
  ggplot(aes(x = Year)) +
    geom_hline(yintercept = target, col = "red") +
    geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
    geom_line(aes(y = OADR), col = "#0000cc") +
    geom_line(data = OADR_history, aes(y = OADR)) +
    facet_grid(. ~ Series) +
    ggtitle("OADR forecasts for boundary pension age schemes") +
    ylab("Old age dependency ratio")
```
